Qualifying Examination Paper

### 2018-11-18 main.tex
181118-0921 ready to submit

%\subsection{Introduction}
The Generative Adversarial Nets (GAN) framework was first introduced by Goodfellow et al. in 2014 \cite{NIPS2014_5423}.  The GAN framework involves the simultaneous training of both a generative model $G$ with parameters $\theta_g$ and a discriminative model $D$ with parameters $\theta_d$.  Given a target data space $T$ with distribution $p_t$, $G$'s task is to learn a mapping from a noisy input $z$ to the data space $T$ ($G:Z \rightarrow G(z) \sim p_g \approx p_t$); while $D$'s task is to discriminate whether some input $x$ originated from either $T$ or $G(z)$ ($D: X \rightarrow \{0, 1\}$).  Since $G$ would like to generate samples that are representative of $T$, and therefore make $D$'s task more difficult by capturing $p_t$ with $p_g$, $G$ includes a loss term that is based on whether $D$ successfully discriminated inputs as $T$ or $G(z)$ and back-propagates $D$'s success as error to $\theta_g$ appropriately.  In this way, $G$ learns how to generate data that is hard for an ever-improving $D$ to distinguish.  Importantly, labeled data is not required for either $G$ or $D$ because the loss function used by $G$ is defined in terms of $D(x)$ and $(1-D(G(z))) \in \{0, 1\}$ (ie. did $G$ fool $D$?) and the labels for $x$ essentially map to $\{p_t, p_g\}$ (ie. from target or generated data?).  Thus, the GAN framework presents a promising approach for generating data that approximates a target distribution in an unsupervised manner.

@@

In the original GAN, $G$ learns to generate data that estimates $p_t$, but cannot target specific sub-distributions within $p_t$, such as class labels or modes within $p_t$.  Shortly after the original GAN was introduced, Mirza and Osindero introduced an extension called Conditional GAN \cite{mirza2014conditional} which addresses this need.  By adding a conditioning input layer to both models $G$ and $D$, one can present the conditioning data $y$ alongside the normal data.  $G$ will learn a mapping from $z$ to $X$ given $y$ that will result in making classification of $X$ given $y$ difficult for $D$.  This advancement seems obvious in retrospect, but warrants contemplation.  While $G$ represents a mapping that captures the distribution of the target data space $T$ in general, the noisy input $z$ can be regarded as the diversity component of the input and $y$ can regarded as the specification component of the input.  Since $y$ is constant within a given mode, a smaller portion of the overall networks for $G$ and $D$ can focus on the generation and discrimination, respectively, of the modal contribution whereas the remaining portions of the networks can focus on the unspecified contributions from $z$.  Of course, Conditional GAN requires that conditioning data (eg. labels) are available for all target samples $x \in X$.

Radford, Metz, and Chintala \cite{DBLP:journals/corr/RadfordMC15} evaluated various model architectures and recommended a set of guidelines and constraints for $G$ and $D$ architectures that appeared to perform well in terms of stability, convergence, resolution, and depth of representation.  These guidelines describe a Deep Convolutional GAN (DCGAN) and are summarized as follows: (a) use convolution and fractional convolution layers with striding to achieve adaptive down-sampling ($D$) or up-sampling ($G$), respectively, rather than fixed/deterministic methods (i.e. max pooling), (b) use batch normalization between convolution layers to mitigate collapse or failure due to poor initialization or vanishing gradients, (c) avoid fully-connected layers, with the exception of the input to $G$ and the output of $D$, to help earlier convergence, and (d) use Rectifier Linear Unit (ReLU) activation for input and hidden layers in $G$, tanh for the output layer in $G$, and Leaky ReLU for all layers in $D$.  In addition to performance improvements, the authors demonstrate that $D$ is able to learn semantically-relevant features that are both explainable (via latent-space walk based validation) and usable (via feature-based supervised classification).  In one case they were able to discover a linear vector in $Z$-space that could control rotation of faces.

@@

Within the theme of semantic learning and generation, Pathak, Krahenbuhl, Donahue, Darrell, and Efros used an adversarial approach to inpaint (fill in missing portions of) images with large extents of missing pixel data \cite{pathakCVPR16context}.  Their architecture is based on an auto-encoder \cite{hinton2006reducing} combined with GAN.  In their approach, the encoder-decoder learns a semantic encoding based on the non-missing portions and attempts to reproduce a whole image based on that semantic encoding.  The `reconstruction loss' is defined in terms of distance ($L_2$) from the filled area to the removed area. The encoder-decoder is regarded as $G$, and a new discriminator $D$ is trained to predict whether its input is a reconstructed output from $G$ or an original image.  Interestingly, and in contrast with \cite{mirza2014conditional}, the authors achieved better results when $G$, but not $D$, was conditioned with context information \footnote{The paper defines context information as the missing pixels which, if true, undermines the objective (any statement of success should be based on withholding the missing pixels from the architecture).  I have requested clarification on this from the author (17 Oct 2018).}.

@@

Luc, Couprie, Chintala and Verbeek applied a straightforward GAN approach to the task of semantic segmentation on images \cite{Luc2016SemanticSU}.  Their approach uses a Convolutional Neural Network (CNN) based generative model $G$ to learn a class label for each pixel in the image based on a ground-truth labeling (supervised), thereby creating a segmentation map of the input image.  $D$ then takes a segmentation map and tries to classify it as being a ground truth map or a generated map.  
%While $D$'s objective function tries to maximize classification accuracy of the input segmentation map as being either ground truth or generated, $G$'s objective function tries to maximize pixel class labeling accuracy with respect to ground truth while also minimizing accuracy.

@@

Reed et al. applied a GAN approach to the dual-task of (1) generating realistic images (2) from text-based descriptions \cite{reed2016generative}.  Essentially, they create $G$ by concatenating the input noise with an encoding of the text description and feed the result into a feed-forward CNN using fractional-striding\footnote{The paper claims this to be a de-convolutional network, but I presume it to mean a CNN using fractional striding to achieve up-sampling.}.  $D$ then down-samples with CNN layers until a 4x4 representation is achieved, concatenates the text encoding onto each of the 16 frames, and continues convolutions to achieve the binary discriminator output.  The learning objectives are consistent with \cite{NIPS2014_5423}.  However, since there are two sources of error (error associated with producing fake-looking images and error associated with producing real-looking images that do not match the description), their approach addresses the second source of error by augmenting the labeled data with real images having non-matching descriptions, which $D$ must learn to recognize.

@@

A logical step forwards from image-based applications is to apply GAN to video.  Mathieu, Couprie, and LeCun first adopted a GAN approach to a video prediction task \cite{Mathieu2015DeepMV}.  They designed a scaled generator $G_k$ that convolves input frames at scale $k$ and predicts a future frame at that scale $Y_k$.  The overall generator $G$ then generates the final predicted frame $Y$ at full resolution using a Laplacian pyramid \cite{denton2015deep} built on each $G_k$.  The discriminator $D$ attempts to classify the last frame(s) in a frame sequence as being either real or generated by $G$ (the first frames in the input sequence are always real), and thus provides the usable adversarial loss to $G$.

Tulyakov, Liu, Yang, and Kautz introduce a method for decomposing video into content (the objects in the video) and motion (the movement of those objects) components, each having its own generator and discriminator ($G_C, G_M, D_C, D_M$) \cite{tulyakov2017mocogan}.  $D_C$ attempts to detect whether a frame is sampled from a real video clip or a generated one, while $D_M$ attempts to detect whether a video clip (series of frames) is sampled from a real or generated clip.  $G_C$ (a CNN) takes motion vectors from $G_M$ (a Recurrent Neural Network), and it's objective includes loss terms from both $D_C$ (a CNN) and $D_M$ (a spatio-temporal CNN), while $G_M$'s objective includes a loss term from $D_M$ only.  In this way, the noise input to $G_C$ can control which objects are in the video, while the noise input to $G_M$ can control the objects' motion.  Another notable application involves segmentation-map-to-video synthesis \cite{wang2018videotovideo}.

@@

As discussed, the GAN approach has enabled major improvements to several research areas including semi-supervised and unsupervised learning, generative models, the learning of complex loss functions, data synthesis for other learning tasks, image and domain learning and translation, and semantic learning and generation.  In general, the GAN approach provides a relatively simple and tractable way of isolating deep learning objectives and sources of error in such a way that they can be addressed individually and researchers can make headway toward a complex objective, as is apparent in the Conditional GAN, in-painting, MoCoGAN, and text-to-image generation, among others.  Broadly stated, as deep learning models adopt more complex architectures and greater capacity, there is an increasing need to provide more meaningful and comprehensive constraint to the model's objective.  GANs provide a tractable methodology for learning sets of constraints which can be as complex as the main learning objective, or even more-so.

@@

Further, as research yields models and approaches that efficiently and effectively solve moderately complex tasks, it is reasonable to expect growing a demand for standardized, modular, and extensible model interfaces (eg. Model Based Engineering ecosystem) for use among research and commercial entities to solve more complex tasks and continue the evolution of artificial intelligence.

In the area of security, GAN approaches pose both a threat (fake video, adversarial examples) as well as a benefit (eg. efficient fuzzing \cite{hu2018ganfuzz}) to security, privacy, and safety.  Specifically, the ability to generate adversarial examples potentially applies to many systems in which the input to that system is corruptible/mutable by a malicious actor.  Unfortunately, deep learning approaches to build robustness against these attacks into the system are only advancing the adversarial game one move forward.  A more effective (though admittedly not immune) approach may involve research into understanding and increasing the robustness of the manifold (hidden layers) of deep learning models.  Some objectives of research in this area may be to level-load the sensitivity of the manifold to small changes or to explore the robustness of the manifold in terms of spacial, temporal, or modal variation.

@@

When ML methods are used as a tool in an adversarial context like security, robustness of the model to adversarial examples becomes a primary design objective.  Intrusion detection systems (IDS) and Spam filters are two classic examples wherein the design objective is to accurate classify messages or traffic as benign or malicious, while the attacker's objective is to design his/her malicious content to be classified as benign (i.e. evade detection).  %This scenario depicts an \textit{exploratory}, \textit{integrity}, and \textit{specific} attack.

@@

Spam filtering is a very real example of this problem, and has a relatively rich history from an adversarial learning perspective.  Word-based Bayesian Spam filters date back to 1998 \cite{sahami1998bayesian}, and the first `Bayes vs. Bayes' attack surfaced (in the public eye) in 2004 \cite{graham2004beat}.  These early examples demonstrated the concept, but were not human-spoofable.  Generating adversarial perturbations that (a) retain the same general Spam content, (b) are not detectable by humans, and (c) result in classification evasion, has proved to be a difficult challenge.  Recently, Iyyer, Wieting, Gimpel, and Zettlemoyer developed an approach known as Syntactically Controlled Paraphrase Networks \cite{DBLP:journals/corr/abs-1804-06059}.  First, they implemented a parse generator which takes, as input, a sentence $s_1$, a full parse $p_1$ of $s_1$ (obtained using \cite{manning2014stanford}), and a target template $t_2$, and provides a target parse $p_2$.  Next, they implemented a paraphrase generator which takes, as input, $s_1$ and $p_2$, and generates a paraphrase sentence $s_2$.  They show that randomly generated paraphrase samples (not adversarially learned) result in a relatively high number of miss-classifications, and also that augmenting those classification models at train-time with these syntactically-diverse adversarial examples results in better performance in the face of new adversarial examples.

@@

Shokri, Stronati, Song, and Shmatikov have demonstrated a methodology to determine whether a specific sample was included within the training set for a target model \cite{shokri2017membership}.  Given a specific data sample $x_?$ and a target model $M_t$, their paper shows how to create multiple `shadow' models with different (real or synthesized) data from that used to train $M_t$, obtain prediction responses from each of the shadow models that can be labeled as `in' or `out' depending on whether each sample was part of that shadow models training set, and then use the labeled response data to train an attack model $M_a$.  After training, $M_a$ achieves good performance in predicting whether black-box responses from $M_t$ are associated with training input (`in') or test input (`out').  The paper addresses the issue of bias from confidence in the responses by synthesizing the data and sampling from the subset of that data that results in similar confidence distributions from $M_t$.

Similarly, Song, Ristenpart, and Shmatikov demonstrated several white- and black-box approaches to build covert channels into ML models for the purpose of extracting sensitive/proprietary training data.  In the attack scenario, the data owner may not wish to reveal the training data to the model developer, but rather have the model trained and delivered by a secure third part.  White-box methods were presented but, more interestingly, a `capacity abuse' attack was described that addresses the black-box scenario.  Essentially, the learning algorithm automatically augments the training data with chosen (by the attacker) data that is labeled with an encoding of the private training data.  The model learns on both the original and malicious training data, and then the attacker, having black-box access to the model, can present the known malicious data to the model and receive the encoded private data via the responses.  I hypothesized that performance of the model for both its benign purpose as well as its covert purpose depends on the malicious data being sparse.  The intuition is that since sparse data is distant  from the private training data (in the feature space), it will not have adverse affects on classification; and since each sparse sample is distant from other sparse samples, they are mutually separable resulting in higher accuracy predictions.  As a follow-up independent study, I demonstrated under ideal conditions that the Membership Inference \cite{shokri2017membership} methodology could be used to detect whether a given model was trained on a sparse distribution or not, thereby serving as a potential indicator of covert channel(s) \cite{stein2018covert}.

@@

ML robustness in the face of adversarial examples is likely to continue being an open problem for some time.  The challenge is not a transient implementation issue that will be worked out as ML technology matures, but rather, like generalization, a core learning issue at the heart of the gap between ML and true intelligence.  In this vein, I feel that a deeper understanding of complex models, specifically deep learning networks, including properties, topographies, and structures, and their effects in adversarial scenarios.  For example, characterizing parameter evolution in the manifold during training on benign data sets vs data sets with adversarial augmentation may reveal indicators that could be measured directly on future models (in the absence of adversarial data).  Further, the formalized approach discussed in \cite{russu2016secure} could be extended to more complex networks.  Since knowledge of the adversary's perturbation minimization objective helped inform provable design guidelines for the classifier, perhaps a finer-grained approach to adversarial learning (eg. segmentation of large generative and classification networks with complex tasks into matched ensembles of smaller networks with simpler tasks) will help increase model robustness to adversarial examples.

\newpage
\section{Privacy Prediction}

Two privacy prediction tasks have been identified: (1) predict whether each pixel in a given image is part of a private object, and (2) predict whether or not a given image has private content\footnote{The tasks are addressed in reverse order from how they were presented in \ref{app:crandall} because, in the approach described herein, the solution for (2) can be largely derived from the solution for (1).}.  For both tasks, assume that $N$ images are sampled, each with $M$ pixels having $H$ channels defined as $I : {\lbrack0,256\rbrack}^{M \times H} \rightarrow \{i_{mh} | \forall m \in \lbrack0,M), \forall h \in \lbrack0,H) \}$.  Also, the following forms of evidence are available for each image $I_n$ sampled from $I$:

@@

Let's define some assumptions.

\begin{enumerate}
    \item Both tasks are semi-supervised, such that the only form of labeled data is $t_n$\footnote{The semi-supervised assumption was adopted because human point-and-click labeling of private image regions for both training and updating of models is thought to be a realistic scenario.}.  Note that this assumption implies that $t_n$ will not be available at test time.
\end{enumerate}

@@

When defining a probabilistic model, it is important to define the central assumptions behind what the model is attempting to capture in terms of privacy. For this approach, the following assumptions are used: (a) certain objects, or object details, are private, and (b) whether an image is private is determined by whether it contains private objects or object details.  Notice that certain contextual privacy scenarios, such as an image of a car known to belong to `Bob' being parked outside of a liquor store during work hours, for example, may not necessarily be marked private, even though `Bob' might argue that it is.

@@

To form the basis of the probabilistic model, a belief network which juxtaposes our evidence and other random variables into the believed set of dependency assumptions can be created. The dependency assumptions are defined as follows.  Firstly, an image ($I$) is the result of, and therefore depends on, the true object-to-pixel mapping ($i_m$ on $o_k$) that is captured by the camera.  Secondly, the scene type ($S$) prediction is based on, and therefore depends on, the image ($I$).  Lastly, we'll assume for now that image meta-data ($D$) in its raw form doesn't meaningfully contribute to the privacy determination problem.  GPS location and time stamps may be useful for influencing the scene probabilities or accounting for lighting differences in the image for object recognition, but we do not have direct influence over those predictors.  The resulting belief network is shown in Figure \ref{fig:belief}.

@@

Time complexity for all algorithms are given in their respective captions.  $N$ is number of images, $M$ is number of pixels per image, $K$ is number of object types, $L_n$ is number of objects in image $I_n$, $Q$ is the number of neighbors to pixels, and $T$ is number of iterations (for root finding). $T$ and $Q$ are presumed to be small.

@@

Equation \ref{eqn:loglik} represents the Log Likelihood of the observed data to be maximized over $\theta$, and Equation \ref{eqn:constr} represents the constraint that prior probabilities for all object types sum to 1.  A Lagrangian (Equation \ref{eqn:lagr}) is constructed to define the boundary on the Log Likelihood along which the constraint is satisfied.  The roots of the vector of first derivatives for this boundary (Equation \ref{eqn:lagr1der}) will contain the prior distribution that maximizes the posterior distribution.  Equation \ref{eqn:lagr1der} is difficult to solve in closed form. Thus, we will use the Newton-Raphson root finding algorithm to estimate the roots in $O(M(NK + K^3 + TNK))$ time, Algorithm \ref{alg:newtraph}.  This algorithm also requires the second derivative of the Lagrangian, a Jacobian matrix, expressed in Equation \ref{eqn:lagr2der}.

>>>>

%\subsection{Introduction}
The Generative Adversarial Nets (GAN) framework was first introduced by Goodfellow et al. in 2014 \cite{NIPS2014_5423}.  The GAN framework involves the simultaneous training of both a generative model $G$ with parameters $\theta_g$ and a discriminative model $D$ with parameters $\theta_d$.  Given a target data space $T$ with distribution $p_t$, $G$'s task is to learn a mapping from a noisy input $z$ to a data space that estimates the target data space $T$ ($G:Z \rightarrow G(z) \sim p_g \approx p_t$); while $D$'s task is to discriminate whether some input $x$ originated from either $T$ or $G(z)$ ($D: X \rightarrow \{0, 1\}$).  Since $G$ would like to generate samples that are representative of $T$, and therefore make $D$'s task more difficult by capturing $p_t$ with $p_g$, $G$ includes a loss term that is based on whether $D$ successfully discriminated inputs as $T$ or $G(z)$ and back-propagates $D$'s success as error to $\theta_g$ appropriately.  In this way, $G$ learns how to generate data that is hard for an ever-improving $D$ to distinguish.  Importantly, `target' or `non-target' (or $\{p_t,p_{g}\}$, respectively) are the only labels (of $x$) required by either $G$ or $D$ because the loss function used by $G$ is defined in terms of $D(t)$ and $(1-D(G(z)))$ (ie. $G$ tries to minimize while $D$ tries to maximize, or vise versa).  Thus, the GAN framework presents a promising approach for generating data that approximates a target distribution in an unsupervised manner.

@@

In the original GAN, $G$ learns to generate data that estimates $p_t$, but cannot target specific sub-distributions within $p_t$, such as class labels or modes within $p_t$.  Shortly after the original GAN was introduced, Mirza and Osindero introduced an extension called Conditional GAN \cite{mirza2014conditional} which addresses this need.  By adding a conditioning input layer to both models $G$ and $D$, one can present the conditioning data $y$ alongside the normal data.  $G$ will learn a mapping from $z$ to $X$ given $y$ that will result in making classification of $X$ given $y$ difficult for $D$.  This advancement seems obvious in retrospect, but warrants contemplation.  While $G$ represents a mapping that captures the distribution of the target data space $T$ in general, the noisy input $z$ can be regarded as the diversity component of the input and $y$ can regarded as the specification component of the input.  Since $y$ is constant within a given mode, a smaller portion of the overall networks for $G$ and $D$ can focus on the generation and discrimination, respectively, of the modal contribution whereas the remaining portions of the networks can focus on the unspecified contributions from $z$.  Of course, Conditional GAN requires that conditioning data (eg. labels) are available for all target samples $t \in T$.

Radford, Metz, and Chintala \cite{DBLP:journals/corr/RadfordMC15} evaluated various model architectures and recommended a set of guidelines and constraints for $G$ and $D$ architectures that appeared to perform well in terms of stability, convergence, resolution, and depth of representation.  These guidelines describe a Deep Convolutional GAN (DCGAN) and are summarized as follows: (a) use convolution and fractional convolution layers with striding to achieve adaptive down-sampling ($D$) or up-sampling ($G$), respectively, rather than fixed/deterministic methods (i.e. max pooling), (b) use batch normalization between convolution layers to mitigate collapse or failure due to poor initialization or vanishing gradients, (c) avoid fully-connected layers, with the exception of the input to $G$ and the output of $D$, to help earlier convergence, and (d) use Rectifier Linear Unit (ReLU) activation for input and hidden layers in $G$, tanh for the output layer in $G$, and Leaky ReLU for all layers in $D$.  In addition to performance improvements, the authors demonstrate that $D$ is able to learn semantically-relevant features that are both explainable (via latent-space walk based validation) and usable (via feature-based supervised classification).  In one example case they were able to discover a linear vector in $Z$-space that could control rotation of faces.

@@

Within the theme of semantic learning and generation, Pathak, Krahenbuhl, Donahue, Darrell, and Efros used an adversarial approach to inpaint (fill in missing portions of) images with large extents of missing pixel data \cite{pathakCVPR16context}.  Their architecture is based on an auto-encoder \cite{hinton2006reducing} combined with GAN.  In their approach, the encoder-decoder learns a semantic encoding based on the non-missing portions and attempts to reproduce a whole image based on that semantic encoding.  The encoder-decoder is regarded as $G$, and a new discriminator $D$ is trained to predict whether its input is a reconstructed output from $G$ or an original image.  The `reconstruction loss' for $G$ is defined in terms of distance ($L_2$) from the filled area to the removed area and the adversrial loss comes from $D$. Interestingly, and in contrast with \cite{mirza2014conditional}, the authors achieved better results when $G$, but not $D$, was conditioned with context information \footnote{The paper defines context information as the missing pixels which, if true, undermines the objective (any statement of success should be based on withholding the missing pixels from the architecture).  I have requested clarification on this from the author (17 Oct 2018) and have not received a response as of 18 Nov 2018.}.

@@

Luc, Couprie, Chintala and Verbeek applied a straightforward GAN approach to the task of semantic segmentation on images \cite{Luc2016SemanticSU}.  Their approach uses a Convolutional Neural Network (CNN) based generative model $G$ to learn a class label for each pixel in the image based on a ground-truth labeling (supervised), thereby creating a segmentation map of the input image.  $D$ then takes a segmentation map and tries to classify it as being a ground truth map or a generated map, and passes its loss back to $G$.  
%While $D$'s objective function tries to maximize classification accuracy of the input segmentation map as being either ground truth or generated, $G$'s objective function tries to maximize pixel class labeling accuracy with respect to ground truth while also minimizing accuracy.

@@

Reed et al. applied a GAN approach to the dual-task of (1) generating realistic images (2) from text-based descriptions \cite{reed2016generative}.  Essentially, they create $G$ by concatenating the input noise with an encoding of the text description and feed the result into a feed-forward CNN using fractional-striding\footnote{The paper claims this to be a de-convolutional network, but I presume it to mean a CNN using fractional striding to achieve up-sampling.}.  The architecture is a variant of the Conditional GAN.  $D$ then down-samples with CNN layers until a 4x4 representation is achieved, concatenates the text encoding onto each of the 16 frames, and continues convolutions to achieve the binary discriminator output.  The learning objectives are consistent with \cite{NIPS2014_5423}.  However, since there are two sources of error (error associated with producing fake-looking images and error associated with producing real-looking images that do not match the description), their approach addresses the second source of error by augmenting the labeled data with real images having non-matching descriptions, which $D$ must learn to recognize.

@@

A logical progression from image-based applications is to apply GAN to video.  Mathieu, Couprie, and LeCun first adopted a GAN approach to a video prediction task \cite{Mathieu2015DeepMV}.  They designed a scaled generator $G_k$ that convolves input frames at scale $k$ and predicts a future frame at that scale $Y_k$.  The overall generator $G$ then generates the final predicted frame $Y$ at full resolution using a Laplacian pyramid \cite{denton2015deep} built on each $G_k$.  The discriminator $D$ attempts to classify the last frame(s) in a sequence as being either real or generated by $G$ (the first frames in the input sequence are always real), and thus provides the usable adversarial loss to $G$.

Tulyakov, Liu, Yang, and Kautz introduce MoCoGAN, a method for decomposing video into content (the objects in the video) and motion (the movement of those objects) components, each having its own generator and discriminator ($G_C, G_M, D_C, D_M$) \cite{tulyakov2017mocogan}.  $D_C$ attempts to detect whether a frame is sampled from a real video clip or a generated one, while $D_M$ attempts to detect whether a video clip (series of frames) is sampled from a real or generated clip.  $G_C$ (a CNN) takes motion vectors from $G_M$ (a Recurrent Neural Network), and it's objective includes loss terms from both $D_C$ (a CNN) and $D_M$ (a spatio-temporal CNN), while $G_M$'s objective includes a loss term from $D_M$ only.  In this way, the noise input to $G_C$ can control which objects are in the video, while the noise input to $G_M$ can control the objects' motion.  Another notable application involves segmentation-map-to-video synthesis \cite{wang2018videotovideo}.

@@

As discussed, the GAN approach has enabled major improvements to several research areas including enablement of semi-supervised and unsupervised learning, improved performance of generative models, the learning of highly complex loss functions, data synthesis for enabling/improving other learning tasks, image and domain learning and translation, and semantic learning and generation.  In general, the GAN approach provides a relatively simple and tractable way of isolating deep learning objectives and sources of error in such a way that they can be addressed individually and researchers can make headway toward a complex objective, as is apparent in the Conditional GAN, in-painting, MoCoGAN, and text-to-image generation, among others.  Broadly stated, as deep learning models adopt more complex architectures and greater capacity, there is an increasing need to provide more meaningful and comprehensive constraint(s) to the model's objective.  GANs provide a tractable methodology for learning sets of constraints (losses) which can be as complex as the main learning objective, or even more-so.

@@

Further, as research yields models and approaches that efficiently and effectively solve moderately complex tasks, it is reasonable to expect an increase in demand for standardized, modular, and extensible model interfaces (eg. Model Based Engineering ecosystem) for use among research and commercial entities to solve more complex tasks and continue the evolution of artificial intelligence.

In the area of security, GAN approaches pose both a threat (eg. fake video, adversarial examples) as well as a benefit (eg. efficient fuzzing \cite{hu2018ganfuzz}) to security, privacy, and safety.  Specifically, the ability to generate adversarial examples potentially applies to many systems in which the input to that system is corruptible/mutable by a malicious actor.  Unfortunately, deep learning approaches to build robustness against these attacks into the system are only advancing the adversarial game one move forward.  A more effective (though admittedly not immune) approach may involve research into understanding and increasing the robustness of the manifold (hidden layers) of deep learning models.  Some objectives of research in this area may be to level-load the sensitivity of the manifold to small changes or to explore the robustness of the manifold in terms of spacial, temporal, or modal variation.

@@

When ML methods are used as a tool in an adversarial context like security, robustness of the model to adversarial examples becomes a primary design objective.  Intrusion detection systems (IDS) and Spam filters are two classic examples wherein the design objective is to accurate classify messages or traffic as benign or malicious in the presence of an attacker who's objective is to design his/her malicious content to be classified as benign (i.e. evade detection).  %This scenario depicts an \textit{exploratory}, \textit{integrity}, and \textit{specific} attack.

@@

Spam filtering is a very real example of this problem, and has a relatively rich history from an adversarial learning perspective.  Word-based Bayesian Spam filters date back to 1998 \cite{sahami1998bayesian}, and the first `Bayes vs. Bayes' publicly-demonstrated attack was presented in 2004 \cite{graham2004beat}.  These early examples demonstrated the concept, but were not human-spoofable.  Generating adversarial perturbations that (a) retain the same general Spam content, (b) are not detectable by humans, and (c) result in classification evasion, has proved to be a difficult challenge.  Recently, Iyyer, Wieting, Gimpel, and Zettlemoyer developed an approach known as Syntactically Controlled Paraphrase Networks \cite{DBLP:journals/corr/abs-1804-06059}.  First, they implemented a parse generator which takes, as input, a sentence $s_1$, a full parse $p_1$ of $s_1$ (obtained using \cite{manning2014stanford}), and a target template $t_2$, and provides a target parse $p_2$.  Next, they implemented a paraphrase generator which takes, as input, $s_1$ and $p_2$, and generates a paraphrase sentence $s_2$.  They show that randomly generated paraphrase samples (not adversarially learned) result in a relatively high number of miss-classifications using a common classifier trained on common data sets, and also that augmenting the training data with these syntactically-diverse adversarial examples results in better performance in the face of new adversarial examples.

@@

The next two papers address the problem of confidentiality of training data used to train models.  An andividual or company may develop and train a model based on data they own and wish to protect, such as financial, medical, social, or other information, while making the model available to those who are not authorized to see the training data.  Shokri, Stronati, Song, and Shmatikov have demonstrated a methodology to determine whether a specific sample was included within the training set for a target model \cite{shokri2017membership}.  Given a specific data sample $x_?$ and a target model $M_t$, their paper shows how to (a) create multiple `shadow' models with different (real or synthesized) data from that used to train $M_t$, (b) obtain prediction responses from each of the shadow models that can be labeled as `in' or `out' depending on whether each sample was part of that shadow models training set, and then (c) use the labeled response data to train an attack model $M_a$.  After training, $M_a$ achieves good performance in predicting whether black-box responses from $M_t$ are associated with training input (`in') or test input (`out').  The paper addresses the issue of bias from confidence in the responses by synthesizing the data and sampling from only the subset of that synthesized data which results in similar confidence distributions from $M_t$.

Similarly, Song, Ristenpart, and Shmatikov demonstrated several white- and black-box approaches to build covert channels into ML models for the purpose of extracting sensitive/proprietary training data.  In the attack scenario, the data owner may not wish to reveal the training data to the model developer, but rather have the model trained and delivered by a secure third party.  White-box methods were presented but, more interestingly, a `capacity abuse' attack was described that addresses the black-box scenario.  Essentially, the malicious learning algorithm automatically augments the training data with attacker-chosen data (think seeded number generator) that is then labeled with an encoding of the private training data just prior to training.  The model learns on both the original and malicious training data.  Later on, the attacker, having black-box access to the model, can present the known malicious data to the model and receive the encoded private data via the responses.  Stein built upon this work, and hypothesized that performance of the model for both its benign purpose as well as its covert purpose depends on the malicious data being sparse. \cite{stein2018covert} The intuition is that since sparse data is distant  from the private training data (in the feature space), it will not have adverse affects on classification; and since each sparse sample is distant from other sparse samples, they are mutually separable resulting in higher accuracy training data reconstruction.  Stein demonstrated under ideal conditions that the Membership Inference \cite{shokri2017membership} methodology could be used to detect whether a given model was trained on a sparse distribution or not, thereby serving as a potential indicator of covert channel(s).

@@

ML robustness in the face of adversarial examples is likely to continue being an open problem for some time.  The challenge is not a transient implementation issue that will be worked out as ML technology matures, but rather, like bias vs variance, a core learning issue at the heart of the gap between ML and true intelligence.  In this vein, I feel that a deeper understanding of complex models, specifically deep learning networks, including properties, topographies, and structures, and their effects in adversarial scenarios, is a promising area of study.  For example, characterizing parameter evolution in the manifold during training on benign data sets vs data sets with adversarial augmentation may reveal indicators that could be measured directly on future models (in the absence of adversarial data).  Further, the formalized approach discussed in \cite{russu2016secure} could be extended to more complex networks.  Since knowledge of the adversary's perturbation minimization objective helped inform provable design guidelines for the classifier, perhaps a finer-grained approach to adversarial learning (eg. segmentation of large generative and classification networks with complex tasks into matched ensembles of smaller networks with simpler tasks) will lead to discovery of better weakness causality and eventually prescriptions for model robustness to specific adversarial goals.

\newpage
\section{Privacy Prediction}\label{sec:privpred}

Two privacy prediction tasks have been identified: (1) predict whether each pixel in a given image is part of a private object, and (2) predict whether or not a given image has private content\footnote{The tasks are addressed in reverse order from how they were presented in \ref{app:questions} because, in the approach described herein, the solution for (2) can be largely derived from the solution for (1).}.  For both tasks, assume that $N$ images are sampled, each with $M$ pixels having $H$ channels defined as $I : {\lbrack0,256\rbrack}^{M \times H} \rightarrow \{i_{mh} | \forall m \in \lbrack0,M), \forall h \in \lbrack0,H) \}$.  Also, the following forms of evidence are available for each image $I_n$ sampled from $I$:

@@

@@

When defining a probabilistic model, it is important to define the central assumptions behind what the model is attempting to capture in terms of privacy. For this approach, the following assumptions are used:

\begin{enumerate}
    \item Both tasks are semi-supervised, such that the only form of labeled data is $t_n$\footnote{The semi-supervised assumption was adopted because human point-and-click labeling of private image regions for both training and updating of models is thought to be a realistic scenario.}.  Note that this assumption implies that $t_n$ will not be available at test time.
    \item Certain objects, or object details, are private.
    \item Whether an image is private is determined by whether it contains private objects or object details.
\end{enumerate}

Notice that certain contextual privacy scenarios, such as an image of a car known to belong to `Bob' being parked outside of a liquor store during work hours, for example, may not necessarily be marked private, even though `Bob' might argue that it is.

@@

To form the basis of the probabilistic model, a belief network which juxtaposes our evidence and other random variables into the believed set of dependency assumptions is created. The dependency assumptions are defined as follows.  Firstly, an image ($I$) is the result of, and therefore depends on, the true object-to-pixel mapping ($i_m$ on $o_k$) that is captured by the camera.  Secondly, the scene type ($S$) prediction is based on, and therefore depends on, the image ($I$).  Lastly, we'll assume for now that image meta-data ($D$) in its raw form doesn't meaningfully contribute to the privacy determination problem.  GPS location and time stamps may be useful for influencing the scene probabilities or accounting for lighting differences in the image for object recognition, but we do not have direct influence over those predictors.  The resulting belief network is shown in Figure \ref{fig:belief}.

@@

All pseudo code can be found in Appendix \ref{app:algs}.  Time complexity for all algorithms is given in their respective captions.  $N$ is number of images, $M$ is number of pixels per image, $K$ is number of object types, $L_n$ is number of objects in image $I_n$, $Q$ is the number of neighbors to pixels, and $T$ is number of iterations (for root finding). $T$ and $Q$ are presumed to be small.

@@

Equation \ref{eqn:loglik} represents the Log Likelihood of the observed data to be maximized over $\theta$, and Equation \ref{eqn:constr} represents the constraint that prior probabilities for all object types sum to 1.  A Lagrangian (Equation \ref{eqn:lagr}) is constructed to define the boundary on the Log Likelihood along which the constraint is satisfied.  The roots of the vector of first derivatives for this boundary (Equation \ref{eqn:lagr1der}) will contain the prior distribution that maximizes the posterior distribution.  Equation \ref{eqn:lagr1der} is difficult to solve in closed form. Thus, we will use the Newton-Raphson root finding algorithm to estimate the roots in $O(M(NK + K^3 + TNK))$ time, Algorithm \ref{alg:newtraph}.  This algorithm also requires the second derivative of the Lagrangian, a Jacobian matrix, expressed in Equation \ref{eqn:lagr2der}.  Essentially, the algorithm uses the hyperplane formed by the gradient at any coordinate to estimate the root as the point at which the plane passes through the axes, and repeats the process using the estimated root until a sufficiently close approximation is reached.

Now that the prior $p(i_m \textrm{ on } o)$ has been estimated, we can use Bayes rule to calculate $p(i_m \textrm{ on } o \mid I)$ as follows:
